### 2019-09-20 bp_results_1.tex
added ref to figure 2

Figure \ref{fig:dailyStress} illustrates these points, showing both participants tendency to report and return to baseline stress levels

>>>>

Figure \ref{fig:dailyStress} illustrates these points, showing both participants tendency to report and return to baseline stress levels, as well
as a distinct difference in baseline stress level (rating 2 for S1 vs rating 3 for S3).
